---
title: "R Markdown Presentation & Plotly"
subtitle: "Developing Data Products"
author: "ECHF"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: arta
      highlightLines: true
      countIncrementalSlides: false
---



```{r setup, include=FALSE}
options(
  htmltools.dir.version  = FALSE,
  htmltools.preserve.raw = FALSE # needed for windows
)
```


### Instructions

#### Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity! 

### Review criteria
#### The rubric contains the following two questions:

1.- Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?

2.- Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?


---
# First sample plotly interactive
```{r include=FALSE}
# load packages
library(ggplot2) # to create plots and feed to ggplotly()
library(plotly)  # to create interactive plots
```
```{r}
# library(plotly)
quakes <- read.csv("https://earthquake.usgs.gov/fdsnws/event/1/query?starttime=2010-01-01T00:00:00&minmagnitude=7&format=csv&latitude=19.42847&longitude=-99.12766&maxradiuskm=6000&orderby=magnitude")
fig <- quakes 
fig <- fig %>%
  plot_ly(
    type = 'densitymapbox',
    lat = ~latitude,
    lon = ~longitude,
    coloraxis = 'coloraxis',
    radius = 10) 
fig <- fig %>%
  layout(
    mapbox = list(
      style="stamen-terrain",
      center= list(lon=260)), coloraxis = list(colorscale = "Viridis"))

```
###### Using this url, we have loaded earthquakes since the start of 2010 that had a magnitude of 7 and above, within a 6,000 kilometer radius of the geographic center of the Mexico city. 

---
# Map Earthquakes
```{r}

fig

```







