---
title: "Shiny Application and Reproducible Pitch"
subtitle: "Developing Data Products"
author: "ECHF"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    font_adjustment: -2
    lib_dir: libs
    nature:
      highlightStyle: arta
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(
  htmltools.dir.version  = FALSE,
  htmltools.preserve.raw = FALSE # needed for windows
)

```
```{css, echo = FALSE}
.remark-slide-content {
  font-size: 10px;
  padding: 2px 8px 2px 8px;
}
.remark-code, .remark-inline-code {
  background: #f0f0f0;
}
.remark-code {
  font-size: 12px;
}
.huge .remark-code { /*Change made here*/
  font-size: 70% !important;
}
.tiny .remark-code { /*Change made here*/
  font-size: 10% !important;
}
```
## Introduction
#### The following APP allows us to visualize earthquakes in North America since 2010 with a magnitude greater than 5. 
```{r evaluate = FALSE}
# used Library
library(shiny)
library(leaflet)
library(RColorBrewer)
# load dataset
quakes <- read.csv("https://earthquake.usgs.gov/fdsnws/event/1/query?starttime=2010-01-01T00:00:00&minmagnitude=5&format=csv&latitude=19.42847&longitude=-99.12766&maxradiuskm=6000&orderby=magnitude")
# turn to data.frame and reshape
quakes <- as.data.frame(quakes)
```
#### Using this url, we have loaded earthquakes since the start of 2010 that had a magnitude of 5 and above, within a 6,000 kilometer radius of the geographic center of the Mexico city.

---
#### uI.R first part of the program where the visualization controls are established and where they are shown. 
.huge[
```{r evaluate = FALSE}
ui <- bootstrapPage(
    tags$style(type = "text/css", "html, body {width:100%;height:100%}"),
    titlePanel("Earthquakes since the start of 2010 that had a magnitude of 5 and above"),
    leafletOutput("map", width = "100%", height = "100%"),
    absolutePanel(top = 100, right = 10,
                  sliderInput("range", "Magnitudes", min(quakes$mag), max(quakes$mag),
                              value = range(quakes$mag), step = 0.1
                  ),
                  selectInput("colors", "Color Scheme",
                              rownames(subset(brewer.pal.info, category %in% c("seq", "div")))
                  ),
                  checkboxInput("legend", "Show legend", TRUE)
    )
)

```
]
---
#### server.R second part of the program where the page is rendered, that is, every time you move the controls, the view will be updated 
```{r evaluate = FALSE}
  # Reactive expression for the data subsetted to what the user selected
  filteredData <- reactive({
    quakes[quakes$mag >= input$range[1] & quakes$mag <= input$range[2],]
  })
  # This reactive expression represents the palette function,
  # which changes as the user makes selections in UI.
  colorpal <- reactive({
    colorNumeric(input$colors, quakes$mag)
  })
  # output$map <- renderLeaflet({
  #   # Use leaflet() here, and only include aspects of the map that
  #   # won't need to change dynamically (at least, not unless the
  #   # entire map is being torn down and recreated).
  #   leaflet(quakes) %>%
  #     addTiles() %>%
  #     setView(lng = -99.12766,
  #             lat = 19.42847,
  #             zoom = 3) 
  # 
  # })

```
---
####  server.R second part of the process where the map is rendered every time  the controls are updated and thus you see the displayed view. 
```{r evaluate = FALSE}
# Incremental changes to the map (in this case, replacing the
  # circles when a new color is chosen) should be performed in
  # an observer. Each independent set of things that can change
  # should be managed in its own observer.
  observe({
    pal <- colorpal()
    
    leafletProxy("map", data = filteredData()) %>%
      clearShapes() %>%
      addCircles(radius = ~6^mag/6, weight = 1, color = "#777777",
                 fillColor = ~pal(mag), fillOpacity = 0.7, popup = ~paste(mag)
      )
  })
  
  # Use a separate observer to recreate the legend as needed.
  observe({
    proxy <- leafletProxy("map", data = quakes)
    
    # Remove any existing legend, and only if the legend is
    # enabled, create a new one.
    proxy %>% clearControls()
    if (input$legend) {
      pal <- colorpal()
      proxy %>% addLegend(position = "bottomright",
                          pal = pal, values = ~mag
      )
    }
  })

```







